\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.6in, right=0.6in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref} % Remove hyperlink borders
\pagestyle{fancy}
\usepackage{lmodern}
\usepackage[spanish]{babel}  % Add this line to use Spanish language


% Define a medium font size
\newcommand{\mediumfont}{\fontsize{12pt}{14pt}\selectfont}

\begin{document}
	
	\pagestyle{fancy}

	% Set footer
	\lfoot{Prepared: \today}
	\rfoot{Page \thepage\ de \pageref{LastPage}\hspace{10pt}\hrule\vspace{10pt}}

	
	\begin{center}
				\textbf{\LARGE Marco Antonio Parra Fernández} \\
			    {\mediumfont MSc. Industrial Engineering / Full-Stack Web Developer} \\

				\begin{minipage}[t]{0.45\textwidth}
					\small +56 9 5629 1334 \\
					\small Chillán, Chile \\
				\end{minipage}%
				\hfill
				\begin{minipage}[t]{0.45\textwidth}
					\raggedleft
        			\small \href{https://portfolio-mparraf.herokuapp.com}{Link to Portfolio-Page} \\
					\small \href{https://www.linkedin.com/in/marco-antonio-parra-82999337/}{Link to LinkedIn} \\
					\small \href{https://www.github.com/maaferna}{Link to GitHub}
				\end{minipage}
				\vspace{10pt} % Adjust the space as needed
				\hrule
				\vspace{10pt} % Adjust the space as needed

	\end{center}
	
	\section*{Professional Profile}
	% Add your professional profile text here
	\small
	Industrial Engineer with over five years of experience in software development and project management. Known for creating innovative solutions in web development and data science, leading teams in the manufacturing industry, and directing technology transfer projects. My focus is on continuous improvement, with applied knowledge in the field of operations management, planning, and production control. My motivation is to develop a career in the IT industry through building and maintaining applications that provide solutions to industry problems. I am a highly motivated professional with exceptional programming skills, a deep understanding of technological trends, and valuable experience contributing to challenging and varied projects.

	
		\section*{Keywords}
	\small
	Full Stack Web Development / Python / Data Analysis / Machine Learning / SQL / HTML / CSS / JavaScript / Data-driven Decision Making
	
	\section*{Education}
	\begin{itemize}[left=0pt]
		\item \textbf{Master of Science in Industrial Engineering} \\
		University of Bío-Bío, 2017-2022. Operations research \& optimization models.
	\end{itemize}
	
	\section*{Specializations/Certifications}
				\small      
			My competencies range from data acquisition and cleaning, analysis and visualization, to database management. In programming, I have solid knowledge in Python, troubleshooting, debugging, Configuration Management, and task automation. I have experience in database architecture, CRUD operations, and SQL queries applied to data science. My skills extend to web development with HTML, CSS3, and JavaScript. Additionally, I have experience in Linux environments and GIT. 

		\begin{itemize}[left=0pt]
			
			\item \textbf{Bootcamp: Desarrollo Full Stack Python Trainee} \\
			Eductecno/Talento Digital, Nov 2023. \textit{\href{https://www.acreditta.com/credential/1654395b-6317-44bf-9beb-18774afdb129}{Link to Credential}}			

			
			\item \textbf{Bootcamp: Desarrollo Ruby On Rails para emprendimientos de tipo Start-Up} \\
			Le-Wagon/Talento Digital, Sep 2021.
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/Emprendimiento web.pdf}{Link to Credential}}	
			
			 \vspace{0.2cm} % Adjust the space between the sections with a light horizontal line
			
			\item \textbf{Análisis de Datos de Google} \\
			Google, Dec 2023.
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/AnalisisDatosGoogle.pdf}{Link to credential}}
			
			\item \textbf{Full-Stack Web Development with React Specialization} \\
			The Hong Kong University of Science and Technology, Oct. 2022.
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/Full-Stack Web Development with React.pdf}{Link to Credential}}
			
			
			\item \textbf{PostgreSQL for Everybody Specialization} \\
			University Of Michigan, Ago  2022
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/PostgreSQL for Everybody Specialization.pdf}{Link to Credential}}
			
			\item \textbf{Web Design for Everybody: Basics of Web Development  Coding} \\
			University Of Michigan, Ago 2022.
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/Web Design for Everybody Specialization.pdf}{Link to Credential}}
			
			\item \textbf{Advanced Django: Mastering Django and Django Rest Framework Specialization} \\
			Codio, Jul 2022.
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/Advanced Django Mastering Specialization.pdf}{Link to Credential}}
			
			\item \textbf{Open Source Software Development, Linux and Git Specialization} \\
			The Linux Fundation, May 2022.
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/Open Source Software Development, Linux and Git.pdf}{Link to Credential}}
			
			\item \textbf{Applied Data Science with Python Specialization} \\
			University Of Michigan, Mar 2022
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/Applied Data Science with Python.pdf}{Link to Credential}}

			\item \textbf{Google IT Automation with Python Professional Certificate} \\
			Google, Mar 2022
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/Google IT  Automation with Python.pdf}{Link to Credential}}
			
			\item \textbf{Python for Everybody Specialization} \\
			University Of Michigan, Ago 2020. \textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/PythonforEverybodySpecialization.pdf}{Link to Credential}}
			
			
			\item \textbf{Learn SQL Basics for Data Science Specialization} \\
			UC Davis University Of California, Abr 2022.
			\textit{\href{https://portfolio-mparraf.herokuapp.com/static/shared/Learn SQL Basics for Data Science Specialization.pdf}{Link to Credential}}
			
	
	\end{itemize}
	
	
	\section*{Skills}
	\textbf{Programming Languages:} Python, JavaScript, Ruby \\
	\textbf{Web Development:} Full Stack Web Development, Django, HTML, CSS, React, NodeJS, RoR, REST Framework, Responsive Web Design, Bootstrap \\
	\textbf{Data Science:} Data Analysis, Machine Learning, Text Mining, Data Visualization, Statistical Analysis, Data Cleaning \\
	\textbf{Data Science and Analysis external libraries:} Numpy, Pandas, Scikit-learn, Networkx, NLTK
	\textbf{Visualization:} Matplotlib \\
	\textbf{Database:} PostgreSQL, MySQ, NoSQL, MongoDB \\
	\textbf{Version Control:} Git  \textbf{Operating Systems:} Linux \\
	\textbf{Other Skills:} Microsoft Excel, Project Management, Troubleshooting, Debugging, Configuration Management \\

	\section*{Work Experience}
	% Add your work experience here
	\begin{itemize}[left=0pt]
		\item \textbf{\large Data Science and Web Development Freelancer:} Self-employed \hfill \textit{Aug 2022 - Present} \\
		\small As a freelance professional specialized in Data Science and Full Stack Web Development, I have undertaken various projects combining data analytics knowledge with the creation and maintenance of web applications. My responsibilities include:
		\begin{itemize}[left=10pt]
			\item Using advanced data science techniques to extract relevant information from a data set.
			\item Designing and implementing interactive and visually appealing web applications that meet user specifications.
			\item Continuing learning and staying updated on the latest trends in both data science and web development.
		\end{itemize}
		
		\item \textbf{\large Freelance Trainer, Microsoft Excel:} Mundo Diferente, Consultancy and Training \hfill \textit{2020 - 2020} \\
		\small As a freelance trainer specialized in Microsoft Excel, I collaborate with Mundo Diferente, Consultancy and Training to deliver high-quality training programs.
		
		\item \textbf{\large Project Engineer:} Forest Institute - University of Concepción \hfill \textit{2011 - 2012}
		\begin{itemize}[left=10pt, topsep=0pt]
			\item Development and implementation of technology transfer programs in SMEs, focusing on operational management and process optimization.
			\item Development of digital applications for data acquisition, processing, and analysis using information technology.
		\end{itemize}
		
		\item \textbf{\large Process Engineer:} CMPC Maderas S.A \hfill \textit{2012 - 2016} 
		\begin{itemize}[left=10pt, topsep=0pt]
			\item Led the optimization of operational efficiency in production processes, ensuring compliance with production plans.
			\item Supervised and rigorously controlled product quality, ensuring continuity of the production process.
			\item Developed and managed key performance indicators to evaluate and improve efficiency in the production process.
			\item Led a team of 50 members, fostering a collaborative environment and ensuring effectiveness in production.
		\end{itemize}
		
		\item \textbf{\large Production Planner:} Arauco S.A \hfill \textit{2017 - 2019} 
		\begin{itemize}[left=10pt, topsep=0pt]
			\item Optimized production plans, efficiently coordinating workflow to maximize operational efficiency.
			\item Controlled current production levels and managed product stock to ensure a smooth supply chain.
			\item Developed and managed key performance indicators to evaluate and improve efficiency in the production process.
			\item Led a team of 30 members, promoting a collaborative environment and ensuring effective execution of production plans.
		\end{itemize}
	\end{itemize}
	

	
\section*{Languages}
		\begin{itemize}
		% Add your work experience here
		\item \textbf{Spanish:} Native Language
		\item \textbf{English:} Level B2 - Professional\\
		\textit{Certificate of Proficiency with LEVEL 8 in platform Open English: "for demonstrating proficiencies that align to Level B2 as described by the Common European Framework for Reference (CEFR) for languages as of this 28th day of August, 2021."}
		
	\end{itemize}
	
	
\end{document}

